# Data Construction

Data for this manuscript come from the 2016 and 2018 DC Area Surveys. More information about the 2016 DC Area Survey can be found [here](http://bit.ly/dcas2016) and the 2018 DC Area Survey can be found [here](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3567219).

```{r load-data}
dataDIR <- '~/work/data/dcas/'
load(paste0(dataDIR,'dcas2016/Dataset/R/DCAS_2016_weighted.Rdata'))
dcas16 <- dcas

load(paste0(dataDIR,'dcas2018/dataset/DCAreaSurvey2018.Rdata'))
dcas18 <- dcas
rm(dcas)

```

## Respondent Selection

**Respondents Living in Multiracial Neighborhoods (DCAS 2016).** The DCAS 2016 data represent two populations: those living in multiracial neighborhoods and those living in disproportionately Latino neighborhoods. This manuscript only used data from the multiracial neighborhoods. I create a variable `quad` to represent these variables ('quad' comes from my [previous description](http://bit.ly/nhoodTrajPaper) of stable multiracial neighborhoods as 'quadrivial neighborhoods'). 

```{r subset-data}
dcas16$quad <- dcas16$neighborhood=='Global Neighborhood'
table(dcas16[,c('neighborhood','quad')]) ##Check variable
dcas16$sample_tract <- droplevels(dcas16$sample_tract)

```

```{r subset-data-bak}
# dcas16$quad <- dcas16$neighborhood=='Global Neighborhood'
# table(dcas16[,c('neighborhood','quad')])
# N_norace <- sum(is.na(dcas$dem.race) & dcas$quad==TRUE)
# dcas <- dcas[!is.na(dcas$dem.race) & dcas$quad==TRUE,]
# dcas$sample_tract <- droplevels(dcas$sample_tract)
# N_quad <- length(dcas$studycase)
# N <- sum(!is.na(dcas$dem.race))
# texcmds[['N']] <- N
```


## Variable Construction



### Dependent Variables

**Neighborhood Satisfaction.** Create neighborhood satisfaction variable (`satisfied`) to represent responses of "Extremely Satisfied" or "Very Satisfied". Check that the variable was created correctly.
```{r variables-satisfied}
dcas16$satisfied <- dcas16$nhd.satisfaction %in% c(
                       'Extremely satisfied','Very satisfied')*1
dcas16$nhdsat <- dcas16$nhd.satisfaction
table(dcas16[, c('nhd.satisfaction','satisfied')]) ##Check variable
table(dcas16[, c('nhd.satisfaction','nhdsat')]) ##Check variable

dcas18$satisfied <- dcas18$nhdsat %in% c('Extremely', 'Very')*1
table(dcas18[, c('nhdsat', 'satisfied')]) ##Checkvariable
```


**Neighborhood improvement.** Create variable (`better`) measuring whether respondent perceives that the neighborhood has improved. Include responses "Much better" and "Somewhat better". Check that variable was created correctly.
```{r variables-better}
betterlabs <- c("Much better", "Somewhat better")
changelabs <- c(
    "Much worse" = "Worse",
    "Somewhat worse" = "Worse",
    "About the same" = "Same",
    "Somewhat better" = "Better",
    "Much better" = "Better"
)
dcas16 <- dcas16 %>%
    mutate(
        better = ifelse(
            is.na(nhd.change), NA, 
            dcas16$nhd.change %in% betterlabs),
        nhdchg = recode_factor(nhd.change, !!!changelabs)
    )
table(dcas16[, c("nhd.change", "better")], useNA="always") ##Check variable
table(dcas16[, c("nhd.change", "nhdchg")], useNA="always") ##Check variable


dcas18 <- dcas18 %>%
    mutate(
        nhdchgbak = nhdchg,
        better = ifelse(
            is.na(nhdchgbak), NA, 
            nhdchgbak %in% betterlabs),
        nhdchg = recode_factor(nhdchgbak, !!!changelabs)
    )
table(dcas18[, c("nhdchgbak", "better")], useNA="always") ##Check variable
table(dcas18[, c("nhdchgbak", "nhdchg")], useNA="always") ##Check variable

```

### Independent Variable

**Race.** Create a race variable measuring four-category, mutually exclusive racial categories. 

```{r independent-variables}
fourraces <- c('white', 'asian', 'black', 'latino')

dcas16 <- dcas16 %>%
    mutate(
        raceeth = recode_factor(dem.race, api = "asian"),
        raceeth = relevel(raceeth, ref="white"),
        raceeth_mi = is.na(raceeth),
        anarace = raceeth %in% fourraces
    )
table(dcas16[, c('dem.race', 'raceeth')], useNA='always') ##Check variable
table(dcas16[, c('dem.race', 'raceeth_mi')], useNA="always")
table(dcas16[, c('dem.race', 'anarace')], useNA="always")

racelabs <- c(
    "White" = "white",
    "Asian/Pac. Islander" = "asian",
    "Black" = "black",
    "Latinx" = "latino",
    "Native American" = "other",
    "Other" = "other"
)
dcas18 <- dcas18 %>%
    mutate(
        raceethbak = raceeth,
        raceeth = recode_factor(raceeth, !!!racelabs),
        raceeth = relevel(raceeth, ref="white"),
        raceeth_mi = is.na(raceeth),
        anarace = raceeth %in% fourraces
    )
table(dcas18[, c('raceethbak', 'raceeth')], useNA="always") ##Check variable
table(dcas18[, c('raceethbak', 'raceeth_mi')], useNA="always")
table(dcas18[, c('raceethbak', 'anarace')], useNA="always")

```


### Control Variables

#### Demographic variables

Create variables for demographic controls. 

**Age.** The age variable (`age`) was calculated by subtracting birth year from 2016. Represents age on December 31, 2016. Center age at 50. 

```{r demographic-variables-age, out.width='45%'}
dcas16$age <- dcas16$dem.age - 50 ## Center at age 50
qplot(dcas16$age, labs=c(title="2016"))

dcas18$age <- dcas18$age - 50
qplot(dcas18$age, labs=c(title="2018"))
```

**Foreign born.** Variable (`forborn`) measuring whether respondent reported being born outside of the United States (reference=no).

```{r demographic-variables-forborn}
dcas16$forborn <- dcas16$dem.forborn
table(dcas16[, c("dem.forborn", "forborn")], useNA='always') ##Check variable

dcas18 <- dcas18 %>%
    mutate(forborn = ifelse(is.na(usborn), NA, usborn=="Another country"))
table(dcas18[, c("usborn", "forborn")], useNA="always") ##Check variable

```

**Male.** Variable measures whether the respondent reported being male. The option "other" was offered to respondents. Two respondents in 2016 and five respondents in 2018 reported other and were counted as missing on this variable.

```{r demographic-variables-male}
dcas16$man <- dcas16$dem.gender.mf=='Male'
table(dcas16[, c('dem.gender', 'man')], useNA='always')

dcas18 <- dcas18 %>%
    mutate(man = recode_factor(
        gender, Male=TRUE, Female=FALSE, `In another way`=NA
    ))
table(dcas18[, c("gender","man")], useNA="always") 

```

**Kids.** Variable (`kids`) measures whether the respondent has any children under the age of 18 living at home. Recode unreasonable values to be missing. 
```{r demographic-variables-kids}
dcas16$kids <- as.numeric(as.character(dcas16$q2)) > 0
dcas16$kids[as.numeric(as.character(dcas16$q2)) > 90] <- NA
table(dcas16[, c('q2', 'kids')], useNA='always')

dcas18$kidsbak <- dcas18$kids
dcas18$kids <- ifelse(!is.na(dcas18$kidsbak), dcas18$kidsbak>0, NA)
table(dcas18[, c('kidsbak', 'kids')], useNA="always")

```

**Married.** Variable (`married`) measures whether respondent is married or in a married-like relationship. 
```{r demographic-variables-married}
dcas16$married <- grepl("Now married", dcas16$dem.marital.stat)
table(dcas16[,c('dem.marital.stat','married')], useNA='always') ##Check recoding

dcas18$marriedbak <- dcas18$married
dcas18$married <- dcas18$marriedbak == "Married"
table(dcas18[, c("marriedbak", "married")], useNA="always") ##Check variable

```

#### Socioeconomic Variables

**Educational attainment.** Create variable (`educ`) measuring educational attainment. Check variable was created correctly. 

```{r economic-variables-educ}
dcas16$educ <- factor(dcas16$dem.educ.attain, order=FALSE) %>% 
                relevel(ref='H.S.')
table(dcas16[, c('dem.educ.attain', 'educ')], useNA='always')

educlabs <- c(
    "Less than HS" = "<H.S.",
    "Did not finish HS" = "<H.S.",
    "HS diploma or GED" = "H.S.",
    "Some college, no degree" = "Some college, no B.A.",
    "Associate\'s degree" = "Some college, no B.A.",
    "Bachelor\'s degree" = "B.A.",
    "Advanced degree" = "M.A.+"
)

dcas18 <- dcas18 %>%
    mutate(
        educbak = educ,
        educ = recode_factor(educbak, !!!educlabs),
        educ = relevel(educ, ref="H.S.")
    )
table(dcas18[, c("educbak", "educ")], useNA="always")

```

**Income.** Create variable (`inc`) measuring income using four levels. 
```{r economic-variables-inc}
# dcas16$inc <- dcas16$dem.income.cat4
# table(dcas16$inc, useNA='always')
# inc_dummies <- paste0('inc',1:4)
# dcas[,inc_dummies] <- lapply(1:4,
#         function(i) {unclass(dcas$dem.income.cat4)==i})
# for(i in 1:4) { ## Check recoding
#     print(table(dcas[,c('dem.income.cat4',paste0('inc',i))]))
# }
# inc_names <- sanitize(levels(dcas$dem.income.cat4))
# inc_names[1] <- paste0("\\emph{Income}&&\\\\", inc_names[1])

# table(dcas18$income, useNA="always")

```

*Missingness on Socioeconomic Variables.* Record how many respondents were missing educational attaiment and income data. 

```{r economic-variables-missing}
texcmds[['miinc16']] <- sum(is.na(dcas16$dem.income.cat4))
texcmds[['miedu16']] <- sum(is.na(dcas16$dem.educ.attain))

texcmds[['miinc18']] <- sum(is.na(dcas18$income))
texcmds[['miedu18']] <- sum(is.na(dcas18$educ))

```

Variable   Missing 2016              Missing 2018
---------- ------------------------- -------------------------
Education  `r texcmds[['miedu16']]`  `r texcmds[['miedu18']]`
Income     `r texcmds[['miinc16']]`  `r texcmds[['miinc18']]`
---------- ------------------------- -------------------------

**Housing tenure.** Create indicator for whether respondent owns their home. 

```{r tenure}
dcas16 <- dcas16 %>%
    mutate(own = hh.own)
table(dcas16[, c("hh.own", "own")], useNA="always")

dcas18 <- dcas18 %>%
    mutate(own = ifelse(is.na(tenure), NA, tenure=="Own"))
table(dcas18[, c("tenure", "own")], useNA="always")

```
#### Neighborhood Experience Variables

**Years in the neighborhood.** Variable (`nhdyrs`) measures how long the respondent reported living in neighborhood.  

```{r nhood-variables-years, out.width='45%'}
dcas16$nhdyrs <- as.numeric(as.character(dcas16$q4)) 
qplot(dcas16$nhdyrs, binwidth=5)

dcas18$nhdyrs <- dcas18$yrsnhd
qplot(dcas18$nhdyrs)

```

**Perceived size of neighborhood.** Create three-category variable that measures perceived neighborhood size. Check that variable was created correctly. 
```{r nhood-variables-nhdsize}
sizelabs <- c(
    `1 to 4 blocks` = "1-9 blocks",
    `5 to 9 blocks` = "1-9 blocks",
    `10 to 25 blocks` = "10-50 blocks",
    `25 to 50 blocks` = "10-50 blocks",
    `More than 50 blocks` = ">50 blocks"
)
dcas16 = mutate(dcas16, nhdsize = recode_factor(nhd.size, !!!sizelabs))
table(dcas16[, c('nhd.size', 'nhdsize')], useNA="always") ## Check variable

names(sizelabs) <- gsub(" to ", "-", names(sizelabs))
dcas18 <- dcas18 %>%
    mutate(
        nhdsizebak = nhdsize, 
        nhdsize = recode_factor(nhdsize, !!!sizelabs)
    )
table(dcas18[, c('nhdsizebak','nhdsize')], useNA="always") #Check variable

```

## Add Neighborhood Context onto Survey Data

Create variables containing neighborhood racial composition types by Census tract. These will be used to analyze data by different racial compositions in 2015. 

```{r racial-composition-types}
dcarea <- dcarea %>%
    mutate(
        w = race.pnhw >= 10,
        b = race.pnhb >= 10,
        l = race.phsp >= 10,
        a = race.papi >= 10,
        q = quad15 == TRUE,

        nhdtype = '',
        nhdtype = ifelse(w, 'w', nhdtype),
        nhdtype = ifelse(b, paste0(nhdtype,'b'), nhdtype),
        nhdtype = ifelse(l, paste0(nhdtype,'l'), nhdtype),
        nhdtype = ifelse(a, paste0(nhdtype,'a'), nhdtype),
        nhdtype = ifelse(race.pnhw > 50, 'w', nhdtype),
        nhdtype = ifelse(race.pnhb > 50, 'b', nhdtype),
        nhdtype = ifelse(race.phsp > 50, 'l', nhdtype),
        nhdtype = ifelse(race.papi > 50, 'a', nhdtype),
        nhdtype = ifelse(quad15, 'quad', nhdtype),
        
        wtype = ifelse(nhdtype=='quad', 'quad', ''),
        wtype = ifelse(nhdtype=='w', 'white', wtype),
        wtype = ifelse(wtype=='' & grepl('w\\w{1}$', nhdtype), 'white-1', wtype),
        wtype = ifelse(wtype=='' & grepl('w\\w{2}$', nhdtype), 'white-2', wtype),
        wtype = ifelse(wtype=='', 'non-white', wtype),
        
        across(starts_with('race'), ~ifelse(.==0, 0, log(./100)), 
               .names='ln{.col}'),
        H = (-1 * (exp(lnrace.pnhw) * lnrace.pnhw +
                   exp(lnrace.pnhb) * lnrace.pnhb +
                   exp(lnrace.phsp) * lnrace.phsp +
                   exp(lnrace.papi) * lnrace.papi  )),
        Hc= (H - mean(H, na.rm=TRUE)) / sd(H, na.rm = TRUE)
                
                
    ) %>%
    select(-starts_with('lnrace'))
```

Append the LTDB 2000 values of Census characteristics and the 2015 values of ACS characterisitcs to each of the DCAS dataframes. The code below constructs a variable, `lntotchg`, that equals the natural log of the change in the non-Hispanic white population from 2000 to 2015. This creates a linearly scaled variable that measures change in the white population that accounts for the size of neighborhoods. 
The 2018 DCAS requires an additional step of appending a list of block-groups for each respondent and then merging based on tracts of sampled respondents.

```{r nhood-context}
## Load LTDB 2000 and merge into DC Area neighborhood tract-level dataset
ltdb <- read_csv('../data/ltdb_std_2000_fullcount.csv',
                 col_types = cols(TRTID10 = 'c')) %>%
    rename_with(tolower) 

nhoods <- dcarea %>%
    mutate(trtid10 = sub('G(\\d{2})0(\\d{3})0(\\d{6})', '\\1\\2\\3', GISJOIN)) %>%
    left_join(select(ltdb, trtid10, nhwht00), by='trtid10') %>%
    mutate(lntotchg = log(nhw15/nhwht00))

## Merge combined 2000 Census/2015 ACS data into 2016 DC Area Survey data
dcas16 <- dcas16 %>%
    mutate(trtid10 = sample_tract) %>%
    left_join(nhoods, by='trtid10')
    

## Merge combined 2000 Census/2015 ACS data into 2018 DC Area Survey data
dcas18bg_fname <- 'dcas2018/source/CensusBlockData_R1049.xlsx'
dcas18bg <- readxl::read_xlsx(paste0(dataDIR, dcas18bg_fname)) %>%
    rename_with(tolower) 

dcas18 <- dcas18 %>%
    full_join(dcas18bg, by='rid') %>%
    mutate(trtid10 = substr(cbg, 1, 11)) %>%
    left_join(nhoods, by='trtid10') 
```

## Data Imputation and Weighting

Select variables to keep that will be used in analysis. Define vectors of identification and numeric variables that will be used for imputation. 
```{r weights-variables}
vars <- c(
          # 'satisfied', 'better',
          'nhdsat', 'nhdchg'
          , 'raceeth'
          , 'age'
          , 'forborn'
          , 'man'
          , 'kids'
          , 'married'
          , 'educ'
          , 'own'
          , 'nhdyrs'
          , 'nhdsize'
          # , 'inc'
)
dcas16 <- dcas16 %>%
    mutate(
        rid = as.character(studycase),
        strata = sample_strata
    )
dcas16$rid <- as.character(dcas16$studycase)
idvars16 <- c('rid','weight', 'strata', 'sample_tract')
nominals <- vars[!(vars %in% c('age', 'nhdyrs'))]

dcas18$rid <- as.character(dcas18$rid)
idvars18 <- c("rid", "weight", "strata")
```

Re-level the tract identification number used for fixed effects to the reference tract is that which has the median level of satisfaction. 

```{r weights-median-tract}
satmu <- dcas16 %>%
    select(sample_tract, satisfied) %>%
    group_by(sample_tract) %>%
    summarize(meansat = mean(satisfied, na.rm=TRUE)) %>%
    arrange(meansat) 
medsatid <- satmu$sample_tract[round(nrow(satmu)/2)] %>% as.character()
dcas16$sample_tract <- relevel(dcas16$sample_tract, ref=medsatid)
# levels(dcas16$sample_tract) ## Not run: Check referencing

```

Create five imputation datasets of survey-weighted data and assign to object `dcas<YR>svy`. For the DCAS 2016 data, include only respondents who live in multiracial neighborhoods in the multiple imputation.  

```{r weights-assign}
set.seed(214518)
idvars <- c('satisfied', 'better', 'anarace')
nhoodvars <- c('nhwht00', 'lntotchg', 'nhdtype', 'wtype', 'H', 'Hc', 
               'race.pnhw')
idvars <- c(idvars, nhoodvars)
dcas16 <- subset(dcas16, neighborhood=="Global Neighborhood") %>%
    mutate(sample_tract=factor(sample_tract))
dcas16mi <- amelia(dcas16[dcas16$neighborhood=="Global Neighborhood", 
                          c(vars, idvars, idvars16)], 
                   m=5, noms=nominals, emburn=c(500, 500), p2s=FALSE, 
                   idvars=c(idvars, idvars16))
dcas16svy <- svydesign(id=~rid, strata=~strata, weights=~weight,
                       data=imputationList(dcas16mi$imputations))

dcas18mi <- amelia(dcas18[, c(vars, idvars, idvars18)], 
                   m=5, noms=nominals, emburn=c(500,500), p2s=FALSE, 
                   idvars=c(idvars, idvars18))
dcas18svy <- svydesign(id=~rid, strata=~strata, weights=~weight,
                       data=imputationList(dcas18mi$imputations))


```

## Center Variables
Center all variables on their DC-area-wide values (estimated using the DCAS 2018 data) in order to create comparable regression values across the two data sets, Subtract the mean of the weighted DCAS 2018 variables from the corresponding variables in both the DCAS 2016 (multiracial neighborhoods) and DCAS 2018 (DC-area) data. This sets the intercept across the two data sets at a corresponding value that represents a white resident with DC-area-wide mean values on all other measures. 

```{r scale-variables}
vars <- c("age", "forborn", "man", "kids", "married", "own", "nhdyrs")
mu18 <- lapply(vars, function(var){
    fm <- as.formula(paste("~", var))
    mu <- coef(MIcombine(with(dcas18svy, svymean(fm, na.rm=TRUE))))
    if(length(mu)==1) return(mu[[1]])
    return(mu[[grep("TRUE$", names(mu))]])
})
names(mu18) <- vars
educ <- coef(MIcombine(with(dcas18svy, svymean(~educ, na.rm=TRUE))))
mu18[paste0("educ", 1:5)] <- educ
nhdsize <- coef(MIcombine(with(dcas18svy, svymean(~nhdsize, na.rm=TRUE))))
mu18[paste0("nhdsize", 1:3)] <- nhdsize


svy.center <- function(df) {
    df %>% update(
        agec       = age - mu18[["age"]],
        forbornc   = as.integer(forborn) - mu18[["forborn"]],
        manc       = as.integer(man) - mu18[["man"]],
        kidsc      = as.integer(kids) - mu18[["kids"]],
        marriedc   = as.integer(married) - mu18[["married"]],
        educall    = model.matrix(~educ),
        educ1c     = educall[, 2] - mu18[["educ1"]],
        educ3c     = educall[, 3] - mu18[["educ3"]],
        educ4c     = educall[, 4] - mu18[["educ4"]],
        educ5c     = educall[, 5] - mu18[["educ5"]],
        educall    = 1,
        ownc       = as.integer(own) - mu18[["own"]],
        nhdyrsc    = nhdyrs - mu18[["nhdyrs"]],
        nhdsizeall = model.matrix(~nhdsize),
        nhdsize2c  = nhdsizeall[, 2] - mu18[["nhdsize2"]],
        nhdsize3c  = nhdsizeall[, 3] - mu18[["nhdsize3"]],
        nhdsizeall = 1
    ) 
}
dcas16svy <- svy.center(dcas16svy)
dcas18svy <- svy.center(dcas18svy)

```

## Save Data

Save R object containing the multiply-imputed survey-weighted data (`dcassvy`), variable names (`vars`), imputation list upon which survey data were created (`dcasmi`), a string representing the diretory containing data (`dataDIR`), and the list of values to export to LaTeX (`texcmds`). 
```{r save-data}
save(vars, dataDIR, texcmds, dcarea,
     dcas16svy, dcas16, dcas16mi, 
     dcas18svy, dcas18, dcas18mi,
     file = '../data/dcassvy.Rdata')

```

