# Data

Data for this manuscript come from the 2016 DC Area Survey. More information about the 2016 DC Area Survey can be found [here](http://bit.ly/dcas2016).

```{r load-data}
dataDIR <- '~/work/data/dcas/dcas2016/'
load(paste0(dataDIR,'Dataset/R/DCAS_2016_weighted.Rdata'))

```

## Variable Construction

### Respondents Living in Multiracial Neighborhoods

The DCAS 2016 data represent two populations: those living in multiracial neighborhoods and those living in disproportionately Latino neighborhoods. This manuscript only used data from the multiracial neighborhoods. I create a variable `quad` to represent these variables ('quad' comes from my [previous description](http://bit.ly/nhoodTrajPaper) of stable multiracial neighborhoods as 'quadrivial neighborhoods').

**///////**

**NOTE: NEED TO SUBSET DATA USING SURVEY COMMAND**

**///////**

```{r subset-data}
dcas$quad <- dcas$neighborhood=='Global Neighborhood'
table(dcas[,c('neighborhood','quad')])
N_norace <- sum(is.na(dcas$dem.race) & dcas$quad==TRUE)
dcas <- dcas[!is.na(dcas$dem.race) & dcas$quad==TRUE,]
dcas$sample_tract <- droplevels(dcas$sample_tract)
N_quad <- length(dcas$studycase)
N <- sum(!is.na(dcas$dem.race))
texcmds[['N']] <- N
```


### Dependent Variables

**Neighborhood Satisfaction.** Create neighborhood satisfaction variable (`satisfied`) to represent responses of "Extremely Satisfied" or "Very Satisfied". Check that the variable was created correctly.
```{r variables-satisfied}
dcas$satisfied <- dcas$nhd.satisfaction %in% c(
                       'Extremely satisfied','Very satisfied')*1
table(dcas[, c('nhd.satisfaction','satisfied')])

## Extremely satisfied (not used in the analysis)
# dcas$extremely_satisfied <- as.numeric(dcas$nhd.satisfaction=='Extremely satisfied')*1
# table(dcas[, c('nhd.satisfaction','extremely_satisfied')])

```

**Neighborhood improvement.** Create variable (`better`) measuring whether respondent perceives that the neighborhood has improved. Include responses "Much better" and "Somewhat better". Check that variable was created correctly.
```{r variables-better}
dcas$better <- dcas$nhd.change %in% c(
                       'Much better', 'Somewhat better')*1
table(dcas[, c('nhd.change','better')])

## Much better (not used in the analysis)
# dcas$much_better <- (dcas$nhd.change=='Much better')*1
# table(dcas[, c('nhd.change','much_better')])

```



<!-- ## Preferences for Other Communities -->
```{r rename-commvars, include=FALSE}
## Change names to have search dimension first and commname second
## Help on regex part: https://stackoverflow.com/questions/952275/regex-group-capture-in-r-with-multiple-capture-groups
# search.vars <- grep('nhd\\.srch.+\\.', names(dcas), value=TRUE)
# new_search_matches <- regmatches(
#     search.vars, regexec('nhd\\.srch\\.(.+)\\.(.+)$', search.vars))
# new_search_names <- sapply(new_search_matches, function(x){
#     paste(rev(x[2:3]), collapse='_')})
# names(dcas)[names(dcas)%in%search.vars] <- new_search_names
# 
# dcas$consider_num <- rowSums(dcas[grep('^cons_', names(dcas))])
# dcas$consider_any <- dcas$consider_num > 0
# dcas$notconsider_num <- rowSums(dcas[grep('^nc_', names(dcas))])
# dcas$notconsider_any <- dcas$notconsider_num >0
```


### Independent Variable

**Race.** Set the reference level of the race variable (`dem.race`) to be whites.
```{r independent-variables}
dcas$dem.race <- relevel(dcas$dem.race, ref='white')
table(dcas$dem.race, useNA='always')

```


### Control Variables

#### Demographic variables

Create variables for demographic controls. 

**Age.** The age variable (`age`) was calculated by subtracting birth year from 2016. Represents age on December 31, 2016. Center age at 50. 

```{r demographic-variables-age, out.width='45%'}
dcas$age <- dcas$dem.age - 50 ## Center at age 50
qplot(dcas$age)
```

**Foreign born.** Variable (`forborn`) measuring whether respondent reported being born outside of the United States (reference=no).

```{r demographic-variables-forborn}
dcas$forborn <- dcas$dem.forborn
table(dcas$forborn, useNA='always')
```

**Male.** Variable measures whether the respondent reported being male. The option "other" was offered to respondents. Two respondents reported other and were counted as missing on this variable.

```{r demographic-variables-male}
dcas$man <- dcas$dem.gender.mf=='Male'
table(dcas[, c('dem.gender', 'man')], useNA='always')
```

**Kids.** Variable (`kids`) measures whether the respondent has any children under the age of 18 living at home. Recode unreasonable values to be missing. 
```{r demographic-variables-kids}
dcas$kids <- as.numeric(as.character(dcas$q2)) > 0
dcas$kids[as.numeric(as.character(dcas$q2)) > 90] <- NA
table(dcas[, c('q2', 'kids')], useNA='always')
```

**Married.** Variable (`married`) measures whether respondent is married or in a married-like relationship. 
```{r demographic-variables-married}
dcas$married <- grepl("Now married", dcas$dem.marital.stat)
table(dcas[,c('dem.marital.stat','married')], useNA='always') ##Check recoding
```

#### Socioeconomic Variables

**Educational attainment.** Create variable (`educ`) measuring educational attainment. Check variable was created correctly. 

```{r economic-variables-educ}
dcas$educ <- factor(dcas$dem.educ.attain, order=FALSE) %>% 
                relevel(ref='H.S.')
table(dcas[, c('dem.educ.attain', 'educ')], useNA='always')
# educ_dummies <- paste0('educ',1:5)
# dcas[,educ_dummies] <- lapply(1:5,
#         function(i) {unclass(dcas$dem.educ.attain)==i})
# for(i in 1:5) { ##Check recoding
#     print(table(dcas[,c('dem.educ.attain',paste0('educ',i))]))
# }
# educ_names <- levels(dcas$dem.educ.attain)
# educ_names[1] <- paste0("\\emph{Educational Attainment}&&\\\\", educ_names[1])
```

**Income.** Create variable (`inc`) measuring income using four levels. 
```{r economic-variables-inc}
dcas$inc <- dcas$dem.income.cat4
table(dcas$inc, useNA='always')
# inc_dummies <- paste0('inc',1:4)
# dcas[,inc_dummies] <- lapply(1:4,
#         function(i) {unclass(dcas$dem.income.cat4)==i})
# for(i in 1:4) { ## Check recoding
#     print(table(dcas[,c('dem.income.cat4',paste0('inc',i))]))
# }
# inc_names <- sanitize(levels(dcas$dem.income.cat4))
# inc_names[1] <- paste0("\\emph{Income}&&\\\\", inc_names[1])
```

*Missingness on Socioeconomic Variables.* Record how many respondents were missing educational attaiment and income data. Reported on page 12 of the manuscript.

```{r economic-variables-missing}
texcmds[['miinc']] <- sum(is.na(dcas$dem.income.cat4))
texcmds[['miedu']] <- sum(is.na(dcas$dem.educ.attain))
```

Variable   Missing
---------- -----------------------
Education  `r texcmds[['miedu']]`
Income     `r texcmds[['miinc']]`
---------- -----------------------

#### Neighborhood Perception Variables

**Years in the neighborhood.** Variable (`nhdyrs`) measures how long the respondent reported living in neighborhood. Center at 10 years and show histogram of values. 

```{r nhood-variables-years, out.width='45%'}
dcas$nhdyrs <- as.numeric(as.character(dcas$q4)) - 10 ## Center at 10 years
dcas$nhdyrsc <- scale(dcas$nhdyrs, scale=FALSE)
qplot(dcas$nhdyrsc)
```

**Perceived size of neighborhood.** Create three-category variable that measures perceived neighborhood size. Check that variable was created correctly. 
```{r nhood-variables-nhdsize}
dcas$nhdsize[unclass(dcas$nhd.size)%in%c(1,2)] <- '1-9 blocks'
dcas$nhdsize[unclass(dcas$nhd.size)%in%c(3,4)] <- '10-50 blocks'
dcas$nhdsize[unclass(dcas$nhd.size)==5] <- '>50 blocks'
dcas$nhdsize <- factor(dcas$nhdsize, 
                        levels=c('1-9 blocks', '10-50 blocks', '>50 blocks'))
dcas$nhdsize <- relevel(dcas$nhdsize, ref='1-9 blocks')
table(dcas[,c('nhd.size', 'nhdsize')], useNA='always') ## Check recoding
```

```{r quad-all-comparison}
# source('dcarea/make-quad-nonquad-comparison-table.R')
```

```{r quad-table, echo=TRUE, include=TRUE}
# kable(quad_tbl, row.names = FALSE)
```

