# Descriptive Analysis

Setup data & environment to analyze. 
```{r setup-analysis-environment}
rm(list=ls())
load('../data/dcassvy.Rdata')
texcmds[['Rversion']] <- paste(R.version$major, R.version$minor, sep='.')

## Functions save multiple imputation objects for use with tidyverse
source('broom_mi.R') 
```

**Note:** The data loaded here were created in the file `analysis/01-variable-data-construction.Rmd`. Due to the stochasticity of the multiple imputations, new data generated by sourcing that file will result in minor differences in the final output. 

The data may be analyzed starting with this file since it removes all objects from the environment and loads the `dcassvy.Rdata` file. 

## Sample Descriptive Statistics
The following code reproduces the Table 2 of the manuscript. 

Create functions to summarize each set of variables. 

`desc`

: Returns the summary of the multiply-imputed survey mean 

`make.desc`

: Returns the table of descriptive statistics

```{r descriptives, echo=FALSE}
desc <- function(dat, x) {
    capture.output(
        res <- summary(MIcombine(
            with(dat, svymean(as.formula(paste0('~',x))))))
    )
    return(res[,1:2])
}

make.desc <- function(dat) {
    ## Independent variable (race)
    d <- desc(dat, 'dem.race')

    ## Demographic variables
    d <- rbind(d, desc(dat, 'age'))
    d['age','results'] <- d['age','results'] + 50
    d <- rbind(d, desc(dat, 'forborn')[2,])
    d <- rbind(d, desc(dat, 'man')[2,])
    d <- rbind(d, desc(dat, 'kids')[2,])
    d <- rbind(d, desc(dat, 'married')[2,])

    ## SES variables
    d <- rbind(d, desc(dat, 'educ')[c(2,1,3:5),])

    ## Neighborhood experience variables
    d <- rbind(d, desc(dat, 'nhdyrs'))
    d['nhdyrs','results'] <- d['nhdyrs','results'] + 10
    d <- rbind(d, desc(dat, 'nhdsize'))

    return(d)
}

```

Make table of descriptive statistics. 
```{r descriptives-table}
d <- make.desc(dcassvy) %>%
    cbind(make.desc(subset(dcassvy, dem.race=='api'))) %>%
    cbind(make.desc(subset(dcassvy, dem.race=='black'))) %>%
    cbind(make.desc(subset(dcassvy, dem.race=='latino'))) %>%
    cbind(make.desc(subset(dcassvy, dem.race=='white'))) %>%
    round(2)

## Remove standard deviations from dichotomous & factor variables
continuous_vars <- grep('age|nhdyrs',rownames(d), perl=TRUE)
d[-continuous_vars,c(2,4,6,8,10)] <- ""

## Remove race descriptives for single-race subsets
d[1:4, 3:10] <- ""

tbl.names <- c(
    '\\emph{Race}&&\\\\White', 'Asian', 'Black', 'Latinx\\vspace{1em}',
    '\\emph{Demographics}&&\\\\Age', 'Foreign Born', 'Man', 'Children present',
    'Married\\vspace{1em}',
    '\\emph{Education}&&\\\\Less than H.S.','H.S. or G.E.D.','Some college',
    'Bachelor\'s degree', 'Professional degree\\vspace{1em}',
    '\\emph{Neighborhood Experience}\\\\Years in Neighborhood',
    'Perceived neighborhood size\\\\1-9 blocks',  '10-50 blocks',
    '>50 blocks'
)

d <- data.frame(tbl.names, d)
descriptive_tbl <- as.table(as.matrix(d))
colnames(descriptive_tbl) <- c('Variable', rep(c('Mean', 'S.D.'),5))
kable(descriptive_tbl)

```

Output descriptive statistics into LaTeX table format. 
```{r descriptives-output}
fname <- 'tables/descriptives.tex'
print.xtable(xtable(descriptive_tbl,
                    caption='Means and standard deviations of independent and control variables',
                    align=c('l','l', rep(c('R{.4in}','R{.4in}'), 5)),
                    label='tab:descriptives'),
             booktabs = TRUE,
             floating.environment = 'sidewaystable',
             caption.placement = 'top',
             include.rownames = FALSE,
             file = fname,
             sanitize.text.function = identity,
             timestamp = '')

## Add group column labels to top row of table into the line after the 
## `\toprule` LaTeX command was issued
colsets <-  paste(
    '& \\multicolumn{2}{p{.8in}}{\\centering \\strong{Total Sample}}'
    , '& \\multicolumn{2}{p{.8in}}{\\centering \\strong{Asians}}'
    , '& \\multicolumn{2}{p{.8in}}{\\centering \\strong{Blacks}}'
    , '& \\multicolumn{2}{p{.8in}}{\\centering \\strong{Latinxs}}'
    , '& \\multicolumn{2}{p{.8in}}{\\centering \\strong{Whites}} \\\\'
)
tbltxt <- readLines(fname)
ruleline <- grep('toprule', tbltxt)
tbltxt <- c(tbltxt[1:ruleline], colsets, tbltxt[(ruleline+1):length(tbltxt)])
writeLines(tbltxt, fname)
```
