# Analysis
```{r setup-analysis-environment}
rm(list=ls())
load('../data/dcassvy.Rdata')
```
## Analytical Approach
For each analysis, ran three models. 

1. Race-only model
2. Race and demographic controls
3. Race, demographic, and neighborhood perception variables

* Can't "prove a null" in this case, so will examine how much overlap there is in the confidence intervals (I need to work on explaining this better; any suggestions would be most welcome) [Create subsection at end of **Analysis** to address "proving the null"?]

```{r reporting-functions}
source('report_models.R')
source('make_projections.R')
get_aic <- function(d, m=5){ ## Record mean and between-model variance of AIC
    aics <- sapply(d, function(x) x$aic)
    return(list(mean=mean(aics), var=var(aics)))
}

MIcombine_aic <- function(m) { ## Combines imputations, including AIC
    aic <- get_aic(m)
    mi <- MIcombine(m)
    mi$aic <- aic
    return(mi)
}

```

## Fixed Effects
```{r tract-clustering}
## Describe clustering of respondents within tracts
tract_Ns <- sapply(unique(dcas$sample_tract), 
                   function(x){nrow(dcas[dcas$sample_tract==x,])})
num_quads <- length(tract_Ns)
N_oneresp <- sum(tract_Ns==1)
tract_Ns_max <- max(tract_Ns)
tract_Nfreq <- as.data.frame(table(tract_Ns))
tract_Ns_hist <- ggplot(tract_Nfreq, aes(x=Freq)) + 
    geom_histogram(binwidth=1) +
    scale_x_continuous(breaks=1:19, labels=1:19) +
    labs(title="Distribution of respondents per tract",
         subtitle="Respondents living in quadrivial tracts, 2016 DCAS")
ggsave('images/distribution-of-tract-sample-sizes.png',plot=tract_Ns_hist,
       height=3, width=4, units='in')
```

The correct test of the hypotheses compares the responses of white residents to those of blacks, Latinos, and Asians, *living in the same neighborhood*. As a result, I include fixed effects for each census tract in which respondents resided. Only one respondent lived in `r N_oneresp` tracts, and were therefore dropped from the analysis. Without these tracts, the number of respondents per tract ranged from 2 to `r tract_Ns_max`.

```{r define-models}
m1 <- 'dem.race + sample_tract '
m2 <- paste0(m1, '+ age + I(forborn*1) + I(man*1) + I(kids*1) + I(married*1) +
                 educ')
m3 <- paste0(m2, '+ nhdyrs + nhdsize')
m4 <- sub('dem\\.race \\+ ','',m3)
```

## Multiple Imputation & Survey Weights
Several variables have a substantial amount of missing data. I used the Amelia package (cite) to create five imputation datasets that will be combined for the final results. I then set up the survey dseign using the list of imputed datasets to account for the complex survey design.

```{r multiple-imputation-functions}
source('broom_mi.R') ## Saves multiple imputation
                     ## objects for use with tidyverse
```

## Descriptive Statistics of Independent & Control Variables
```{r descriptives}
desc <- function(x, d=descriptives) {
    vals <- MIcombine(with(dcassvy, svymean(as.formula(paste0('~',x)))))
    return(data.frame(mean=vals$coefficients, se=sqrt(diag(vals$variance))))
}

## Independent variable (race)
d <- desc('dem.race')
tbl.names <- c("\\emph{Race}&&\\\\White", "Asian", "Black", "Latinx")

## Demographic variables
d <- rbind(d, desc('age'))
d <- rbind(d, desc('forborn')[2,])
d <- rbind(d, desc('man')[2,])
d <- rbind(d, desc('kids')[2,])
d <- rbind(d, desc('married')[2,])

tbl.names <- c(tbl.names, 
               c('\\emph{Demographics}&&\\\\Age', 'Foreign Born', 'Man', 
                 'Children present', 'Married'))

## SES variables
d <- rbind(d, desc('educ')[c(2,1,3:5),])
tbl.names <- c(tbl.names,
               c('\\emph{Education}&&\\\\Less than H.S.','H.S. or G.E.D.',
                 'Some college', 'Bachelor\'s degree', 'Professional degree'))

## Neighborhood experience variables
d <- rbind(d, desc('nhdyrs'))
d <- rbind(d, desc('nhdsize'))

tbl.names <- c(tbl.names, 
               '\\emph{Neighborhood Experience}\\\\Years in Neighborhood', 
               '1-9 blocks', '10-50 blocks', '>50 blocks')

## Make table of descriptives
d <- round(d, 2)
continuous_vars <- grep('age|nhdyrs',rownames(d), perl=TRUE)
d[-continuous_vars,'se'] <- ''
d <- data.frame(tbl.names, d)
descriptive_tbl <- as.table(as.matrix(d))
colnames(descriptive_tbl) <- c('Variable', 'Mean', 'S.D.')
```

```{r descriptive-output, echo=TRUE, include=TRUE}
kable(xtable(descriptive_tbl), row.names=FALSE)

print.xtable(xtable(descriptive_tbl,
                    caption='Un-weighted means and standard deviations of independent and control variables',
                    align=c('l','l','p{.5in}','p{.5in}'), label='tab:descriptives'),
             booktabs=TRUE,
             caption.placement='top',
             include.rownames=FALSE,
             file='tables/descriptives.tex',
             sanitize.text.function = identity,
             timestamp='')
```

# Results 

## Satisfaction in Multiethnic Neighborhoods

### Bivariate Analysis
Plot the mean value of satisfaction by each racial group using survey weights.

```{r dependent-descriptives}
mean_satisfied <- MIcombine(with(dcassvy,
                                 svymean(~satisfied)))
summary(mean_satisfied)
```
Overall, `r round(coef(mean_satisfied)[2], 2)*100` percent of residents in the sample were either very or extremely satisfied with their neighborhoods.

```{r satisfaction-bivariate}
satisfied_means <- MIcombine(with(dcassvy,
                                  svyby(~satisfied, ~dem.race, svymean)))
satisfied_ci <- 1.96*sqrt(diag(satisfied_means$variance))
satisfied_vals <- data.frame(dem.race=c('White','Asian','Black','Latinx'),
                             satisfied=coef(satisfied_means),
                             ci=satisfied_ci)
satisfied_plt <- ggplot(satisfied_vals, aes(x=dem.race, y=satisfied)) +
    geom_errorbar(aes(ymin=satisfied-ci, ymax=satisfied+ci), width=0.1) +
    geom_point() +
    scale_y_continuous(limits=c(0,1), breaks=seq(0,1,.20)) +
    labs(y='Proportion', x='Race')
satisfied_plt
ggsave('images/satisfied_descriptive.png', plot=satisfied_plt,
       height=3, width=4, units='in')
```

```{r report-satisfied-bivariate-plot, echo=TRUE, include=TRUE}
satisfied_plt
```

(I plan to make this plot show the un-adjusted and adjusted results)

### Multivariate Analysis
**Satisfied.**

```{r satisfied-analysis, warning=FALSE, results='hide'}
m0_sat <- with(dcassvy,
               svyglm(satisfied ~ sample_tract), family=binomial)
m0_sat <- MIcombine_aic(m0_sat)

m1_sat <- with(dcassvy,
               svyglm(as.formula(paste('satisfied ~',m1)), family=binomial))
m1_sat <- MIcombine_aic(m1_sat)

m2_sat <- with(dcassvy, svyglm(as.formula(paste('satisfied ~', m2)),
                               family=binomial))
m2_sat <- MIcombine_aic(m2_sat)

m3_sat <- with(dcassvy, svyglm(as.formula(paste('satisfied ~', m3)), 
                               family=binomial))
m3_sat_racewald <- lapply(m3_sat, regTermTest, test.terms=~dem.race, df=NULL)
sat_wald_F <- summary(sapply(m3_sat_racewald, function(x) x$Ftest))
sat_wald_p <- summary(sapply(m3_sat_racewald, function(x) x$p))
m3_sat <- MIcombine_aic(m3_sat)

m4_sat <- with(dcassvy, svyglm(as.formula(paste('satisfied ~', m4)),
                               family=binomial))
m4_sat <- MIcombine_aic(m4_sat)
```

```{r report-satisfaction-analysis, echo=TRUE, include=TRUE}
regression_labels <- c('Asian','Black','Latinx',
                       'Age','Foreign Born','Male',
                       'Children Present', 'Married',
                       levels(dcas$dem.educ.attain)[c(1,3:5)],
                       # levels(dcas$dem.income.cat4)[c(1,3:4)],
                       'Years in neighborhood',
                       '10-50 blocks', '>50 blocks')
sat_tbl <- report_models(m1_sat, m2_sat, m3_sat, m4_sat, reglabels=regression_labels,
                         caption=paste0('Estimated coefficients predicting ',
                                        ' neighborhood satisfaction'),
                         label='tab:satisfaction')
sat_tbl
cat(to_latex(sat_tbl), file='tables/satisfaction.tex')
```

Those who perceived their neighborhoods to be 1-9 blocks were `r round(exp(coef(m3_sat)['nhdsize1c']),3)` as likely to find satisfaction in their neighborhood. Those who perceived their neighborhoods to be greater than 50 blocks were `r round(exp(coef(m3_sat)['nhdsize3c']),3)` as likely to find satisfaction, but the difference was not distinguishable from those who perceived their neighborhoods to be between 10 and 50 blocks.
