# Perceptions of Neighborhood Change

## Descriptive analysis of percieved neighborhood change

Calculate overall percentages of repondents who reported that their neighborhood had gotten better, worse, and stayed the same. 

```{r chg-means}
chgmeans <- with(dcas16svy, svymean(~nhdchg, na.rm=TRUE)) %>%
    MIcombine() %>%
    summary() %>%
    mutate_at(1:4, ~.*100)
kable(chgmeans, digits=1)

```

Plot values measuring the percentage of respondents who reported that their neighborhood had gotten better, worse, and stayed the same. 

```{r chg-levels}
chglevs <- c("Worse", "Same", "Better")
chgmeans_tbl <- with(dcas16svy, 
                 svyby(~nhdchg, ~raceeth, svymean, na.rm=TRUE)) %>%
    MIcombine()%>% summary() %>%
    as_tibble() %>%
    mutate_at(1:4, ~.*100) %>%
    mutate(
        raceeth = relevel(factor(
            rep(c("White", "Asian", "Black", "Latino"), 3)), ref="White"),
        nhdchg = ordered(rep(chglevs, each=4), levels=chglevs)
    )
names(chgmeans_tbl) <- c("mean", "se", "lci", "uci", "missinfo", "raceeth", 
                     "nhdchg")

dodge_wd <- .25
chg_plt <- ggplot(chgmeans_tbl, aes(x=nhdchg, y=mean, color=raceeth, shape=raceeth)) +
    geom_point(position=position_dodge(width=dodge_wd), size=2.25) +
    geom_linerange(aes(ymin=lci, ymax=uci), position=position_dodge(dodge_wd)) +
    scale_color_grey(start=0.4, end=.7) +
    scale_shape_manual(values=c(15:18)) +
    labs(
        x = NULL,
        y = "Percent",
        color = NULL, 
        shape = NULL
    ) +
    theme_minimal() +
    theme(
        legend.position = "bottom",
        panel.grid.major.x = element_blank()
    )

chg_plt_cap <- paste(
    "Percent of respondents who report how neighborhood has changed in",
    "past five years by race"
)

```

```{r chg-plt, fig.cap=chg_plt_cap, echo=FALSE}
chg_plt

ggsave("images/nhood_change.pdf", plot = chg_plt,
       width=6.75, units='in')

```

## Regression analyses of perceived neighborhood change

Follow the same process of model development as with the models of within-neighborhood satisfaction. Report the results of all four models. To ease the interpretation of the results, report only models 1 & 3 in the paper. 

```{r chg-regression, warning=FALSE}
## Note: "non-integer #successes" warnings suppressed
m1ch <- with(dcas16svy, svyglm(
    as.formula(paste('better ~', m1)), family=binomial)
)

m2ch <- with(dcas16svy, svyglm(
    as.formula(paste('better ~', m2)), family=binomial)
)

m3ch <- with(dcas16svy, svyglm(
    as.formula(paste('better ~', m3)), family=binomial)
)

m4ch <- with(dcas16svy, svyglm(
    as.formula(paste('better ~', m4)), family=binomial)
)

ch_tbl <- report_models(
    MIcombine_aic(m1ch), MIcombine_aic(m2ch),
    MIcombine_aic(m3ch), MIcombine_aic(m4ch),
    caption = paste(
        "Logistic regression coefficients and standard errors predicted",
        "for models estimating neighborhood improvement among residents",
        "of mulitracial neighborhoods"
    ),
    label = "tab:change",
    reglabels = regression_labels,
    use.headers = TRUE
)
statrow <- nrow(ch_tbl)-3
ch_tbl_pres <- ch_tbl[,c(1,2,4)] %>%
    insert_row(c("Tract fixed effects", rep("X", 2)), after=statrow) %>%
    set_top_border(statrow+1, everywhere, TRUE) %>%
    set_top_border(statrow+2, everywhere, FALSE) %>% 
    set_top_padding(0) %>%
    set_bottom_padding(0)
cat(
    sub("\\(\\\\#(tab:.+?)\\)", "\\\\label{\\1\\}", to_latex(ch_tbl_pres)),
        file="tables/change.tex"
)
ch_tbl

```

Calculate average marginal effects of race on neighborhood change based on results of model 3.  

```{r ch-mfx}
m3ch_mfx <- MImargins(m3ch, param="margins") %>%
    mutate_at(vars(val, SE), ~.*100) %>%
    mutate(p = pnorm(abs(val/SE), lower.tail=FALSE))
kable(m3ch_mfx, digits=c(0,1,1,3))

```

