# Description of DC-Area & Multiracial Neighborhood Populations

The following provides information about the DC Area cited in the manuscript. It includes code that creates Table 1 that compares demographic characteristics of multracial neighborhoods in the DC Area to all neighborhoods in the DC Area. Data come from the IPUMS National Historical Geographic Information System ([NHGIS][]).[^nhgis-cite]

[NHGIS]: https://www.nhgis.org/

[^nhgis-cite]: Steven Manson, Jonathan Schroeder, David Van Riper, and Steven Ruggles. IPUMS National Historical Geographic Information System: Version 13.0 [Database]. Minneapolis: University of Minnesota. 2018. http://doi.org/10.18128/D050.V13.0

Set up environment for analyzing data from the Census. Note the difference between `DATADIR` created here and `dataDIR` created in [Data Construction]. The data files are separated by category and are stored in separate directories, whose names are stored in `vartypes`. 
```{r dcarea-setup}
DATADIR <- '../data/dcarea/tracts/'

vartypes <- c(
    'children-present',
    'educ-attainment',
    'foreign-born',
    'marital-status',
    'median-age',
    'race-ethnicity'
)

## HELPER FUNCTIONS
## Load DC Area data for category of variable
dcarea.data <- function(vartype) {
    f <- paste0(DATADIR, '2010/tabular/', vartype, '/dataset/tracts-2010TIGER-', 
                vartype, '.csv')
    return(read.csv(f))
}

## Return 2-item vector containing mean and standard deviation of variable
meansd <- function(var) {
    return(c(mean=mean(var, na.rm=TRUE), sd=sd(var, na.rm=TRUE)))
}

```

Load data from the ACS 2011-2015 and the 1980 Census to analyze.
```{r dcarea-data}
## Load and join data from different categories of variables from 2015 ACS
dcarea <- lapply(vartypes, dcarea.data) %>%
    reduce(left_join, by='GISJOIN') %>%
    select('GISJOIN', ends_with('15'))

## Load data from 1980
fname <- paste(DATADIR, '1980/tabular/', 'race-ethnicity/dataset',
                'tracts-1980TIGER-race-ethnicity.csv', sep='/')
dcarea80 <- read.csv(fname)

```

## DC-area characteristics 

Population of the DC area.

: Calculate the total population of the DC area in 1980 and 2015. 

```{r dcarea-totpop}
totpop80 <- sum(dcarea80$totpop)
totpop15 <- sum(dcarea$totpop15)

```
   Year    Total Population
   ------  --------------------------------------------------------
   1980    `r prettyNum(totpop80,big.mark=",",scientific=FALSE)`
   2015    `r prettyNum(totpop15,big.mark=",",scientific=FALSE)`
   
Racial composition in 1980. 

: Calculate proportion of DC-area population made up each racial group in 1980.

```{r dcarea-race-1980}
dcarea80 <- sapply(dcarea80[,c('totpop', 'nhw','nhb','hsp','api')], sum)
prace80 <- round(sapply(dcarea80[2:5], function(x) x/dcarea80[1]),3)*100
kable(prace80)

```

Racial composition in 2015. 

: Calculate proportion of DC-area population made up of each racial group in 2015.

```{r dcarea-race-2015}
n.hsp <- sum(dcarea$hsp15)
n.api <- sum(dcarea$api15)
n.nhw <- sum(dcarea$nhw15)
n.nhb <- sum(dcarea$nhb15)
n.totpop <- sum(dcarea$totpop15)

p.hsp <- n.hsp/n.totpop
p.api <- n.api/n.totpop
p.nhw <- n.nhw/n.totpop
p.nhb <- n.nhb/n.totpop

dcarea.race <- data.frame(
    race=c('Latinx','Asian','Non-Hispanic white', 'Non-Hispanic black'),
    vals=round(c(p.hsp, p.api, p.nhw, p.nhb),3)*100)
kable(dcarea.race)

```

Foreign Born

: Calculate percentage of residents that are foreign-born in DC area in 2015 (referenced on page 8 of the manuscript). 
```{r dcarea-forborn}
sum(dcarea$fbpop15)/sum(dcarea$totpop15)

```

Countries of orgin.

: Report largest three countries of origin in the DC area. Load data and keep only tracts in the DC area. 
```{r dcarea-origin-1}
## Analyzes foreign-born population to find top three nations of origin
## among foreign-born population in the DC area

## Source file with function to construct variables for DC area
source('dcarea/dcarea_functions.R')

## Load file of 2015 ACS data on tract-level foreign-born population
fname <- 'dcarea/AC52015_foreign_born.csv'
fborn <- read.csv(fname)

## Select only DC-area tracts
dc.fborn <- select.dcarea(fborn)
```

Create list of variable names that define regions, not countries and keep variables not in the list of regions (which define countries). 
```{r dcarea-origin-2}
region.vars <- c(
    'ADU4E001', 'ADU4E002', 'ADU4E003', 'ADU4E004', 'ADU4E005',
    'ADU4E013', 'ADU4E021', 'ADU4E028',
    'ADU4E047', 'ADU4E048', 'ADU4E049', 'ADU4E056', 'ADU4E067', 'ADU4E078',
    'ADU4E091', 'ADU4E092', 'ADU4E098', 'ADU4E101', 'ADU4E106', 'ADU4E109',
    'ADU4E117', 'ADU4E118',
    'ADU4E123', 'ADU4E124', 'ADU4E125', 'ADU4E138', 'ADU4E148', 'ADU4E160'
)

## Keep only non-region variables
nonregion.vars <- names(dc.fborn)[!(names(dc.fborn) %in% region.vars)]
dc.fborn <- dc.fborn[, nonregion.vars]

```

Sum total population across DC-area tracts by each country of origin, then rank and report the top three countries. The codes (variable names) for the countries can be found in the file `analysis/dcarea/nhgis0011_ds216_20155_2015_tract_E_codebook.txt`. Report the top three DC-area countries of origin (reported by variable name).

```{r dcarea-origin3}
country.sums <- sapply(dc.fborn[, grep('^ADU4', names(dc.fborn), value=TRUE)],
                       function(x) sum(as.numeric(x)))

# Rank countries of origin by population size
country.rank <- sort(country.sums, decreasing=TRUE)

# Report countries of origin by variable name
kable(head(country.rank, 3))

```

Educational Attainment among Foreign-Born Residents

: Report the percentage of U.S. and DC-area residents with BA or graduate degrees by foreign-born status. 
```{r dcarea-educforborn}
## Source file with function to construct variables for DC area
source('dcarea/dcarea_functions.R')

## Load file of 2015 ACS data on tract-level foreign-born population
fname <- 'dcarea/AC52015_educ_by_foreign_born.csv'

fbeduc <- read.csv(fname)
us.fbba <- sum(fbeduc$fbba, na.rm=TRUE) / sum(fbeduc$fbtot25o, na.rm=TRUE)
us.fbgr <- sum(fbeduc$fbgr, na.rm=TRUE) / sum(fbeduc$fbtot25o, na.rm=TRUE)

dc.fbeduc <- select.dcarea(fbeduc)
dc.fbba <- (
    sum(dc.fbeduc$fbba, na.rm=TRUE) / sum(dc.fbeduc$fbtot25o, na.rm=TRUE))
dc.fbgr <- (
    sum(dc.fbeduc$fbgr, na.rm=TRUE) / sum(dc.fbeduc$fbtot25o, na.rm=TRUE))

fbeduc.comp <- data.frame(degree=c('BA', 'MA+'),
                          DC=round(c(dc.fbba, dc.fbgr),3)*100,
                          US=round(c(us.fbba, us.fbgr),3)*100)

kable(fbeduc.comp)
```

## Multiracial neighborhood characteristics

Population living in multiracial neighborhoods

: Report the number of people living in multiracial neighborhoods in 2015. 
```{r dcarea-quadpop}
(quadpop <- sum(dcarea[dcarea$quad15==TRUE, 'totpop15'], na.rm=TRUE))

```

Comparison of multiracial to all DC-area neighborhoods.

: Construct table comparing characteristics of the population living in DC-area multiracial neighborhoods to the characteristics of all DC-area neighborhoods. Code creates Table 1 in the manuscript. Save the comparison table to `tables/nhood_descriptives.tex`.

```{r dcarea-comparison}
## Construct variables for analytic table, and keep only those variables
dcarea <- dcarea %>% mutate(
    ## Children present in HH
    pchildpres = pchpr15 * 100,

    ## Educational attainment
    peduc.lhs = plh15 * 100,
    peduc.hs = phs15 * 100,
    peduc.somecoll = (psc15 + paa15) * 100,
    peduc.ba = pba15 * 100,
    peduc.ma = pgr15 * 100,

    ## Foreign-born
    pfborn = fbpop15 / totpop15 * 100,

    ## Currently married
    pmarried = pmar15 * 100,

    ## Median age (no new variable necessary)

    ## Race-ethnicity
    race.papi = papi15 * 100,
    race.phsp = phsp15 * 100,
    race.pnhb = pnhb15 * 100,
    race.pnhw = pnhw15 * 100
) %>%
    select(GISJOIN, totpop15, pchildpres, pfborn, pmarried, mdage15,
           starts_with('peduc'), starts_with('race'), quad15, nhw15)

## CONSTRUCT TABLE
## Define list of variables in desired display order
tablevars <- c(grep('^race', names(dcarea), value=TRUE),
               grep('^peduc', names(dcarea), value=TRUE),
               'pfborn', 'pchildpres', 'pmarried')

## Create table of values for multiethnic and all DC Area tracts
quads <- t(sapply(dcarea[dcarea$quad15==TRUE, tablevars], meansd))
tracts <- t(sapply(dcarea[, tablevars], meansd))
tracttbl <- data.frame(quads, tracts)

## List of variable names to be published in the table
tblnames <- c('\\emph{Racial composition}&&&\\\\Percent Asian',
              'Percent Hispanic',
              'Percent non-Hispanic black',
              'Percent non-Hispanic white',
              '\\emph{Educational attainment}&&&\\\\Percent less than high school',
              'Percent high school',
              'Percent some college', 'Percent bachelor\'s degree',
              'Percent professional degree',
              '\\emph{Other demographic characteristics}&&&\\\\Percent foreign-born',
              'Percent of households with children present',
              'Percent married (not separated)'
)

## Create table with formatting
tbl <- data.frame(tblnames, quads, blank=rep(' ', nrow(quads)), tracts)
tbl[,c(2,3,5,6)] <- lapply(tbl[,c(2,3,5,6)], function(x) sprintf('%3.1f', x))
# tbl[,c(3,6)] <- lapply(tbl[,c(3,6)], function(x) paste0('(',x,')'))
colnames(tbl) <- c('Variable', 'Mean', 'S.D.','', 'Mean', 'S.D.')

cap <- paste0('Means and standard deviations of tract-level variables',
              'in multiethnic and quadrivial neighborhoods in the DC Area')
kable(tbl, 
      caption=cap, row.names=FALSE)

```

```{r dcarea-comparison-latex, echo=FALSE, include=FALSE}
## Write table to file
fname <- 'tables/nhood_descriptives.tex'
quad_tbl <- xtable(tbl,
                   caption='Means and standard deviations of tract-level variables in multiracial neighborhoods in the DC Area',
                   align=c('l','p{2in}','R{4em}','R{4em}','p{1em}','R{4em}','R{4em}'),
                   label='tab:nhddescriptives')
print.xtable(quad_tbl,
             booktabs=TRUE,
             caption.placement='top',
             include.rownames=FALSE,
             file=fname,
             sanitize.text.function = identity,
             timestamp='')
colsets <- paste('&\\multicolumn{2}{p{8em}}{\\centering Multiethnic neighborhoods}&',
                 '&\\multicolumn{2}{p{8em}}{\\centering All neighborhoods}\\\\ ')
tbltxt <- readLines(fname)
tbltxt <- c(tbltxt[1:8], colsets, tbltxt[9:length(tbltxt)])
writeLines(tbltxt, fname)

```

Location of multiracial neighborhoods in the DC area

: Rank counties by the number of multiracial neighborhoods included in their jurisdictions. Multiracial neighborhoods were those in which Asians, blacks, Latinxs, and whites all made up at least 10% of the neighborhood populaiton *and* no group represents a majority.

    Construct variables measuring multiracial neighborhoods, both those included using the criteria and those excluded for not meeting the criterion that no group be a majority. 
```{r dcarea-inclusion}
racevars <- paste0('race.',c('papi','pnhb','phsp','pnhw'))
dcarea$othmulti <- apply(sapply(dcarea[, racevars],
                                function(x) !is.na(x) & x>=10), 1, all)
dcarea$exclmulti <- dcarea$quad15 != dcarea$othmulti
dcarea$county <- factor(substr(as.character(dcarea$GISJOIN), 2, 7))
levels(dcarea$county) <- c(
    'D.C.'
    , 'Montgomery county'
    , 'Prince George\'s county'
    , 'Arlington county'
    , 'Fairfax county'
    , 'Fairfax city'
    , 'Falls Church city'
    , 'Alexandria city'
)

## Breakdown of 'excluded' multiethnic neighborhoods by county
excl_juris <- table(dcarea[, c('county', 'exclmulti')])
N_excluded <- sum(excl_juris[,2])

## Breakdown of multiethnic neighborhoods by county
multi_tbl <-table(dcarea[, c('county', 'quad15')])
kable(sort(multi_tbl[,2], decreasing=TRUE))

```

## Diverse neighborhoods excluded for having a majority race

There were `r N_excluded` neighborhoods that did not meet the criterion that no racial group be a majority. 

*Excluded for having a white majority*

```{r dcarea-exclusion-white}
dcarea[!is.na(dcarea$exclmulti) & dcarea$exclmulti==TRUE & dcarea$race.pnhw>50,
       c('county', racevars, 'GISJOIN')]
```

*Excluded for having a black majority*

```{r dcarea-exclusion-black}
dcarea[!is.na(dcarea$exclmulti) & dcarea$exclmulti==TRUE & dcarea$race.pnhb>50,
       c('county', racevars, 'GISJOIN')]
```

*Excluded for having a Latino majority:*

```{r dcarea-exclusion-latino}
dcarea[!is.na(dcarea$exclmulti) & dcarea$exclmulti==TRUE & dcarea$race.phsp>50,
       c('county', racevars, 'GISJOIN')]

```
