---
title: "Satisfaction and Stability in Multiethnic Neighborhoods"
author: "Michael Bader"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: 
    bookdown::html_book:
        toc: yes
    bookdown::pdf_book:
        keep_tex: yes

---

# Introduction

Multiethnic neighborhoods have emerged as a common feature in U.S. metropolitan areas during the past half century. Federal anti-discrimination laws, changing racial attitudes, and increased immigration created new opportunities for people to become neighbors with people across multiple racial and ethnic categories. Once exceptional, racial integration among the four largest racial and ethnic groups in the United States has become one of the most common forms--and in some metropolitan areas, *the* most common form--of neighborhood racial change since the 1970s and 1980s **[cite: Logan & Zhang; Bader & Warkentien]**. In a nation beset by its history of racial discrimination and resulting segregation, multiethnic neighborhoods offer hope for a more integrated future. 

Academic research has not kept pace with the growing presence of multiethnically integrated neighborhoods in American metropolitan areas. A small body of qualitative works studying the unique dynamics of integrated neighborhoods provides valuable insight**[w.ch]** into the dynamics of racial integration. But research on neighborhood gentrification and the concentration of poverty has dwarfed that which focuses on this emergent form of neighborhood change. **[Focus on theory, not policy]: Without systematic research on multiethnic neighborhoods, any predictions about the sustainability of this newfound integration will be imprecise and insufficient to inform policies to maintain multiethnic integration.** 

To help build the body of evidence on multiethnic neighborhoods, this article examines whether residents of all races feel equally satisfied living in multiethnic neighborhoods. It does so among a representative sample of residents living in multiethnic neighborhoods in the Washington, D.C. area, a major metropolitan area in the United States with a large number of multiethnic neighborhoods. Evidence from the sample shows that satisfaction is quite high, and that whites are similarly satisfied living in multiethnic neighborhoods as their Asian, black, and Latino neighbors. The findings also show, however, mixed evidence that multiethnic segregation will remain sustainable in the future as the neighborhoods continue to change. The findings reveal directions of future research and possible policy intervention that might be necessary to understand and promote racial integration in the coming decades. 


# Background

Multiethnic neighborhoods came about as Asian, black, and Latinx newcomers moved into neighborhoods that had been all white, or nearly so, starting in the 1980s **(cite: Logan; Bader)**. The trend accelerated in the 1990s and 2000s. Unlike past decades where the entry of non-white residents sparked violence and white flight that caused racial transitions, many whites stayed put as their neighborhoods integrated around them. The number of neighborhoods shared among white, Asian, black, and Latinx neighbors rose rapidly in the 1990s and 2000s. Logan and Zhang estimate that **TK%** of neighborhoods in 2010 were what they termed "global neighborhoods." Similarly, Bader and Warkentien found stable multiethnic integration represented between **TK%** and **TK%** of neighborhoods in the metropolitan areas of the four largest cities. 

Several currents made the growth of multiethnic neighborhoods possible. Federal legislation, especially the Fair Housing Act, made housing discrimination a federal crime. The impact of the FHA, which was passed in 1968 in the wake of the Rev. Dr. Martin Luther King, Jr.'s assassination, was neither immediate nor universal. Racial discrimination has persisted in more subtle ways such as real-estate agents "steering" clients to neighborhoods. The FHA provided, however, provided a legal mechanism for people of color to enter white neighborhoods and challenge overt forms of discrimination. 

Second, *multiethnic* integration would be impossble without a multiethnic population. Increased immigration from Asian and Latin American countries increased the number of Asian and Latinx people in the United States. Immigration unsettled the stark black-white divide in many American metropolitan areas. The trend**[w.ch]** was most pronounced in metropolitan areas that became "new immigrant" destinations in the 1980s and 1990s. The growing economies that attracted migrants also required new housing construction to accomodate growing populations that made integrated neighborhoods possible from the get-go**[w.ch.]**. 

Finally, racial attitudes have been changing. 


## Satisfaction and Long-Term Stability

### Satisfaction and Mobility

Neighborhood satisfaction influences whether people stay put in their neighborhoods. The process of white flight can be described as whites having acted on the immediate and strong feelings of dissatisfaction that the entry of a black family prompted. As whites vacated their houses, additional black families--who were dissatisfied being forced to live in overcrowded ghettos through law and custom--filled those vacancies. The process resulted in the rapid "succession" of the neighborhood's composition from all-white to all-black.

The more sanguine attitudes whites hold about people of color could mean that whites are now satisfied living in integrated neighborhoods. If so, then there is a stronger prospect of long-term integration. Evidence is mixed. On the one hand, patterns of neighborhood change seem to bear this out, with little evidence of rapid racial succession since the 1980s. On the other, studies consistently show lower levels of satisfaction among whites who live in neighborhoods in which people of color make up an increasing share of their neighbors. 

Existing studies of satisfaction among residents measure the composition of racial groups separately or measure the composition of all non-white residents grouped into a single category. **[cite findings here]** Multiethnic neighborhoods represent a distinctive form of integration not captured by the method of measuring racial compositions of groups. Instead, the *presence* of all four racial groups distinguishes these neighborhoods and satisfaction among residents of different races in these distinctive neighborhoods have not been measured.

* Are groups equally satisifed living in integrated neighborhoods, and therefore likely to stay (maintaining integration)?

Measuring whether residents think that the neighborhood has improved provides an additional measure of satisfaction. While satisfied residents might not feel compelled to leave, they could be more inclined to leave if they perceive less improvement in the neighborhood. Previous research shows that white perceptions of neighborhood trends diminish with increasing non-white composition. Even if whites feel satisfied living in neighborhoods, they might feel less confident that they will be satisfied in the future. If true, then whites might be enticed to leave the neighborhood more readily than neighbors of color. Again, however, existing studies do not sample *multiethnic* neighborhoods. 


### Long-Term Stability

Even residents satisfied living in their neighborhood will find themselves exiting for reasons unrelated to the racial composition of the neighborhood. Residents will get married, retire, have children, get divorced, and, in the most extreme case, exit upon their death. Life course transitions such as these cause most moves; and, as residents move out for those reasons, new residents will move in. Satisfaction will be insufficient to predict future integration because integration will survive only as long as the current cohort of residents does. To maintain the multiethnic diversity of the neighborhood therefore requires that the racial composition of households *leaving* multiethnic neighborhoods approximates the racial composition of those *entering* multiethnic neighborhoods. 

Multiethnic neighborhoods must attract racially diverse newcomers to maintain  integration. Residents currently residing in multiethnic neighborhoods provide an obvious clientele to fill vacancies in multiethnic neighborhoods. Yet, we have neither a sense whether current residents of multiethnic neighborhoods would consider moving to another multiethnic neighborhood, nor whether the proportion who would consider another multiethnic neighborhood differs across racial groups. 

Rather than being individually derived or collectively negotiated within households, housing preferences reflect a deeply social process. Households cannot engage with the housing market across an entire metropolitan area. Krysan and Crowder show that people approach housing searches based on word of mouth that shape what people think about different communities, and whether they even know anything about the community at all. Settling on which neighborhoods to consider--and which not to waste time considering--reflects social networks that are segregated by race. Differences in the knowledge residents use as starting points for their housing searches can help us predict the future stability of multiethnic integration. 

Race influences the familiarity residents have with communities and where residents consider moving. Whites know more about and desire moving to neighborhoods with larger shares of white residents. Whites differ from other racial groups, who have stronger desires for integration than whites. Havekes and colleagues find that racial composition influences white searches more at each stage of the search process. They find that whites move to communities with lower shares of whites on average than communities that they search which, in turn, have lower shares of whites on average than communities whites report considering. Multiethnic neighborhoods might expose white residents to more diverse social networks and increase the probability that whites would consider another multiethnic neighborhood. But, again, we have no evidence one way or the other among residents living in multiethnic neighborhoods. 

### Hypotheses

In light of this evidence, this article examines two hypotheses:

1. Whites living in multiethnic neighborhoods will be a) less satisfied with their neighborhoods and b) less likely to perceive neighborhood improvement compared to their Asian, black, and Latinx neighbors; and
2. Whites living in multiethnic neighborhoods will be will be a) less familiar with, b) less likely to consider, and c) more likely to never consider moving to other multiethnic neighborhoods in their metropolitan area compared to their Asian, black, and Latinx neighbors. 


<!--# Setup-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, include=FALSE, message=FALSE)
```

```{r libraries, message=FALSE}
rm(list=ls())
print(R.version.string)
library(Amelia)
library(broom)
library(ggplot2)
library(huxtable)
library(knitr)
library(mitools)
library(survey)
library(tidyverse)
library(xtable)
```




