---
title: "Satisfaction and Stability in Multiethnic Neighborhoods"
author: "Michael Bader"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: 
    bookdown::html_book:
        toc: yes
    bookdown::pdf_book:
        keep_tex: yes

---

# Motivation
This file documents the analysis for the paper "Satisfaction and Stability in Multiethnic Neighborhoods." The paper analyzes data from the 2016 DCAS to examine the level of satisfaction that residents who identify as different races have living in racially integrated neighborhoods. The sample represents people living in two types of neighborhoods: *quadrivial* (whites, blacks, Latinos, and Asians each make up 10% of the population and no group is a majority). 



# Introduction
Multiethnic neighborhoods have emerged as a common feature in U.S. metropolitan areas during the past half century. Federal anti-discrimination laws, changing racial attitudes, and increased immigration created new opportunities for people to become neighbors with people across multiple racial and ethnic categories. Once exceptional, racial integration among the four largest racial and ethnic groups in the United States has become one of the most common forms--and in some metropolitan areas, *the* most common form--of neighborhood racial change since the 1970s and 1980s **[cite: Logan & Zhang; Bader & Warkentien]**. In a nation beset by its history of racial discrimination and resulting segregation, multiethnic neighborhoods offer hope for a more integrated future. 

Academic research has not kept pace with the growing presence of multiethnically integrated neighborhoods in American metropolitan areas. A small body of qualitative works studying the unique dynamics of integrated neighborhoods provides valuable insight**[w.ch]** into the dynamics of racial integration. But research on neighborhood gentrification and the concentration of poverty has dwarfed that which focuses on this emergent form of neighborhood change. Without systematic research on multiethnic neighborhoods, any predictions about the sustainability of this newfound integration will be imprecise and insufficient to inform policies to maintain multiethnic integration. 

To help build the body of evidence on multiethnic neighborhoods, this article examines whether residents of all races feel equally satisfied living in multiethnic neighborhoods. It does so among a representative sample of residents living in multiethnic neighborhoods in the Washington, D.C. area, a major metropolitan area in the United States with a large number of multiethnic neighborhoods. Evidence from the sample shows that satisfaction is quite high, and that whites are similarly satisfied living in multiethnic neighborhoods as their Asian, black, and Latino neighbors. The findings also show, however, mixed evidence that multiethnic segregation will remain sustainable in the future as the neighborhoods continue to change. The findings reveal directions of future research and possible policy intervention that might be necessary to understand and promote racial integration in the coming decades. 


# Background

* **Growth of Multiethnic Neighborhoods** (where to put motivation for studying neighborhood satisfaction and previous research on the topic)
    * Racial segregation has declined steadily across metropolitan areas in the United States, but the level of segregation remains high. The metropolitan trends result from two patterns of racial change in the neighborhoods that compose those metropolitan areas.
        * Growing multiethnic integration.
            * Starting in the 1990s, Asian, Latino, and black residents have moved to some all-white neighborhoods. 
            * Process has been stable as whites have not left as residents of color moved in
            * Logan & Zhang estimate **TK%** of neighborhoods are "global neighborhoods"
            * Bader & Warkentien use the term "quadrivial neighborhoods" and estimate **TK%** of neighborhoods in four large metropolitan areas are multiethnically integrated
            * These neighborhoods are found in places that did not necessarily actively court racial integration
        * The high levels of racial segregation also show that whites are not moving *to* integrated neighborhoods
            * Single-race non-white neighborhoods are second highest percentage of neighborhoods (cite: Friedman)
            * Studies of individual preferences and behavior show that whites overwhelmingly consider and ultimately move to neighborhoods with larger proportions of whites
            * Unlike decades past where violence and white flight marked racial transitions, the process occurs over many decades
    * The process of transition in single-race neighborhoods leads to questions about the long-term stability of multiethnic integration. 
        * The slow rate of transition indicates that whites seem satisfied living in neighborhoods that integrate around them
        * But, when it comes time for whites to move, they are less likely than people of color to move to integrated neighborhoods
        * Suggests that multiethnic neighborhoods would remain integrated as long as the whites living there when people of color move in, but will not be able to sustain that integration without new whites who move into the neighborhoods
        * Yet, it's possible that residents of multiethnically integrated neighborhoods, having experienced multiethnic integration, might be awakened to a new preferences. We don't know because of three "shortcomings" of previous research
            * Past studies have not examined satisfaction of residents across races in *multiethnically* integrated neighborhoods; this has stemmed in part from having insufficient samples of residents living in multiethnically integrated neighborhoods. (Even if they have become more common, they still only make up **TK**% of neighborhoods)
            * Previous research has also focused on compositions of individual racial groups rather than multiethnic composition
            * A similar problem has marked previous research on preferences for neighborhoods; they have not examined preferences for multiethnic neighborhoods
* **Hypotheses**
The paper examines three hypotheses: 

1. Whites will be less likely to be satisfied living in integrated neighborhoods than other racial groups, and they will be much less likely to be extremely satisfied;
2. Whites will be less likely to believe that their neighborhoods have improved compared to other racial groups; and
3. Whites will be less likely to consider moving to other multiracial neighborhoods in the Washington, DC area. 

<!--# Setup-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, include=FALSE, message=FALSE)
```

```{r libraries, message=FALSE}
rm(list=ls())
print(R.version.string)
library(Amelia)
library(broom)
library(ggplot2)
library(huxtable)
library(knitr)
library(mitools)
library(survey)
library(tidyverse)
library(xtable)
```




